\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-17 paper/relatedwork.tex
paper: minor fix on bayesdb language

BayesDB \cite{mansinghka2015bayesdb} provides users with a simple interface to 
leverage statistical inference techniques in a database. Non-experts
can use a simple declarative language, akin to SQL, to specify models
which allow missing value imputation, amongst other broader functionality.
Experts can further customize strategies and express domain knowledge to
improve performance and accuracy.

>>>>

BayesDB \cite{mansinghka2015bayesdb} provides users with a simple interface to 
leverage statistical inference techniques in a database. Non-experts
can use a simple declarative language (an extension of SQL), to specify models
which allow missing value imputation, amongst other broader functionality.
Experts can further customize strategies and express domain knowledge to
improve performance and accuracy.
